%------------------------------------------------------------------------------
\def\todaysdate{20230225}
\newday{\todaysdate}\label{\todaysdate}

Completed dry run with water of the new 15 gallon system.

%------------------------------------------------------------------------------
\def\todaysdate{20230318}
\newday{\todaysdate}\label{\todaysdate}

\newentry[Brew]{0930 Brew Day}

\begin{itemize}
    \item Mixed up a batch of sanitizer with 1 gallon of hot tap water and 1 tbsp of One Step.
    \item Assembled brew hoses and fixtures - using left side of plate chiller for wort
\end{itemize}

\begin{table}[H]
  \centering
  \begin{tabular}[t]{ll}
      \multicolumn{2}{c}{Fermentables} \\
      \hline
      Amount & Fermentable \\
      \hline
      14lbs & Marris Otter Malt \\
      2lbs & Aromatic Malt \\
      1lb & Special B Malt \\
      1lb & Caramel Malt 60L \\
      1lb & Caramel Malt 80L \\
      1lb & Biscuit Malt \\
      0.5lb & Chocolate Malt \\
  \end{tabular}
    \begin{tabular}[t]{lll}
      \multicolumn{3}{c}{Boil Additions} \\
      \hline
        Amount & Addition & Boil Time \\
      \hline
        2oz & Challenger & -60 minutes \\
        5g  & Irish Moss & -15 minutes \\
        2oz & Willamette & -5 minutes \\
  \end{tabular}
  \begin{tabular}[t]{ll}
      \multicolumn{2}{c}{Mash Schedule} \\
      \hline
      Temperature & Time \\
      \hline
      154\degree F & 60 minutes \\
  \end{tabular}
\end{table}

\begin{description}
    \item[0930] 
    \item[1115] Added 13 Gallons in the mash tun.  Set temperature to 158.  
    \item[1220] At temp, set temp to 154, did not drop below mashed in.
    \item[1230] Mash in complete, started 1 hour timer.
    \item[1330] Raised temperature to 210 and raised the malt pipe up.
    \item[1400] Removed malt pipe, placed empty hop spider into kettle to break surface tension and reduce risk of boil over.

\textbf{Pre-boil SG: 1.035}
\textbf{Pre-boil Volume: 12 gallons}

    \item[1520] Boil Started. Added challenger hops to hop spider.
    \item[1605] Added Irish moss (With 15 Minutes left in Boil)
    \item[1615] Added Willamette hops (With 5 Minutes left in Boil).  Turned on recirculation pump to sanitize the plate chiller.
    \item[1200] Boil ended.  Transfer and oxygenate to primary fermentation and pitched yeast.
    \item[1355] Finished Cleaning
    \item[Target OG:] 1.060
    \item[Target Temperature:] 68
    \item[Actual OG: 1.045] 
    \item[Actual Temperature: 65] 
    \item[Volume Collected: 7 gallons] 
\end{description}


%------------------------------------------------------------------------------
\def\todaysdate{20230923}
\newday{\todaysdate}\label{\todaysdate}

Setting up cider for fermentation.

Cleaned the new 60L fermentation vessel.

Added the custom blow-off valve, and cut a length of beer tube to reach from the exhaust of the blow off valve to a 1 gallon milk jub that will sit next to h fermentation vessel.

Using 23 jugs of 86 fl oz Motts 100\% apple juice, 21 lbs of brown sugar, and one packet of M2 Lallemand yeast.

Added 3 jugs (86 fl oz each) and placed on top of a hot plate.  Added 21 lbs of brown sugar and turned the heat all th way up.


